%
% File acl2014.tex
%
% Contact: giovanni.colavizza@epfl.ch
%%
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}

%\setlength\titlebox{5cm}

% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.


\title{Where you should not eat in Chicago}

\author{Lucas Délez \\
  {\tt lucas.delez@epfl.ch} \\\And
  Stanislas Furrerr \\
  {\tt stanislas.furrer@epfl.ch} \\\And
  Luis De Lima \\
  {\tt luis.carvalho@epfl.ch} \\\And
  Yura Tak\\
{\tt yura.tak@epfl.ch} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
  This project aims to study the Chicago Food Inspections Data and report the results of the analysis on this dataset. Our goal is to qualify a zone if it's safe to eat there or not.
\end{abstract}

\section{Introduction}

From the dataset preprocessed at first, we create 2 dataframes : one with all the restaurants and other food establishments, and one with only 5 most inspected chains restaurants (McDonald's, Subway, Starbucks, Taco Bell, Dunkin Donuts). And for each of these dataframes, we analyze the number of inspections, the types of violations and the risk to get finally the map of the Chicago with the scoring of each zone based on these analysis.

\section{Description}

\subsection{Data Preprocessing}
First, we select only elements of dataset that we are interested in : namely the name, facility type, risk, localisation, inspection date, inspection type, result of the inspection and the violations. We process the rows with empty values and also we preprocess the value of each element to be uniform. And finally, for the plotting part, we add the spatial coordinates to the dataframe.



\subsection{Violation Analysis}



\subsection{Inspection Analysis}
For each of the dataframes we get from the preprocessing part, the inspection count per facility type and per chain restaurant has been analyzed. We observe that there is a diminution of the inspections for all facilities types and for all the chain restaurants. And the most frequent inspection type observed is the canvass. For restaurants, we observe lot of inspections by complaints especially in McDonald's.


\subsection{Risk Analysis}


\subsection{Results}



\subsection{Graphics}

{\bf Illustrations}: Place figures, tables, and photographs in the
report near where they are first discussed, rather than at the end, if
possible.  Wide illustrations may run across both columns.

{\bf Captions}: Provide a caption for every illustration; number each one
sequentially in the form:  ``Figure 1. Caption of the Figure.'' ``Table 1.
Caption of the Table.''  Type the captions of the figures and 
tables below the body, using 11 point text.

\begin{thebibliography}{}

\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
Alfred~V. Aho and Jeffrey~D. Ullman.
\newblock 1972.
\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
\newblock Prentice-{Hall}, Englewood Cliffs, NJ.

\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
{American Psychological Association}.
\newblock 1983.
\newblock {\em Publications Manual}.
\newblock American Psychological Association, Washington, DC.

\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
{Association for Computing Machinery}.
\newblock 1983.
\newblock {\em Computing Reviews}, 24(11):503--512.

\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
\newblock 1981.
\newblock Alternation.
\newblock {\em Journal of the Association for Computing Machinery},
  28(1):114--133.

\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
Dan Gusfield.
\newblock 1997.
\newblock {\em Algorithms on Strings, Trees and Sequences}.
\newblock Cambridge University Press, Cambridge, UK.

\end{thebibliography}

\end{document}
